Designing Turk Experiments for Visual Statistical Inference

### 2012-08-22 paper_turk.tex
worked on introduction

It has been found that the visual test, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}. To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}. The Turk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple. In this paper we present how we deal with this trouble and conduct our experiment.

@@

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

>>>>

It has been found that the visual statistical inference \cite{buja:2009}, which does not have distributional assumptions, has the power comparable to the conventional tests \cite{Majumder:2011}. To examine the power of visual statistical inference we recruited human subjects from Amazon Mechanical Turk \cite{turk} for evaluating lineups \cite{buja:2009, Majumder:2011}. The Turk website is designed to recruit workers for simple and easy tasks. Even though the task of evaluating lineups is easy, the technical design of the experiment is complex and the tools available to design this from Turk website is just too simple. In this paper we present an alternative way to conduct the survey by designing a separate web site and getting turk worker do their job from this web site. We also present the simulation experiment design to estimate the power of visual statistical inference.

@@

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

As shown in figure \ref{fig:turk_work_flow} turk workers have to visit the experimental web site and give their consent to participate the survey as per IRB requirement. In the experimental web, there is a option for observers to try some sample lineups to get familiar with the experiment. Once the observers start evaluating the lineups they are sequentially shown a specific number of lineups and at the end they are given a code as a proof for their tusk completion. The payment of the turk worker is processed if they post the code they got from experimental web site. The observers are also asked to provide some demographic information about them to make sure that the code is generated.
